Get utilization standards and piece size by FMU and township

### 2021-09-29 analysis/get_util_piece_size.Rmd
3 significant digits in piece_size

```{r libraries, echo=FALSE, message=FALSE}
#setwd("/home/gwa/Work/historical-residue/Analysis")
setwd("/mnt/chromeos/GoogleDrive/SharedDrives/FES_Data_Sharing_Forestry/Manuscripts/histressupp/analysis")

@@

```{r read data files, echo=FALSE}
util_std <- read.csv(file = '../data/util_std.csv')
piece_size <- read.csv(file = '../data/piece_size.csv')
fmu_twp <- read.csv(file ='../data/FMU_TWP.csv')
species_prop <- read.csv(file = '../data/species_proportions_full.csv') %>%
  select(TRM,max_species)

@@

util_piece <-full_join(util_std,piece_size,by=c("FMU","CD"))
util_piece_fmu_twp <- full_join(util_piece,fmu_twp,by=c("FMU","CD"))
util_piece_fmu_twp$piece_size <- 1/util_piece_fmu_twp$logspm3
util_piece_fmu_twp_species <- full_join(util_piece_fmu_twp,species_prop,by="TRM")
util_piece_fmu_twp_species <- subset(util_piece_fmu_twp_species, (FMU != "A14") &(FMU != "A15") &(FMU != "W11")& (FMU != "W13"))

subs <- subset(util_piece_fmu_twp, (!is.na(piece_size)) & (!is.na(areaha)) & (CD == "Decid"))
avepieceD <- weighted.mean(subs$piece_size,subs$areaha,na.rm = TRUE)

subs <- subset(util_piece_fmu_twp, (!is.na(piece_size)) & (!is.na(areaha)) & (CD == "Conif"))
avepieceC <- weighted.mean(subs$piece_size,subs$areaha,na.rm = TRUE)

>>>>

```{r libraries, echo=FALSE, message=FALSE}
#setwd("/home/gwa/Work/historical-residue/Analysis")
setwd("f:/Shared Drives/FES_Data_Sharing_Forestry/Manuscripts/histressupp/analysis")

@@

```{r read data files, echo=FALSE}
util_std <- read.csv(file = '../data/util_std.csv')
piece_size <- read.csv(file = '../data/piece_size.csv')
piece_size <- select(piece_size,-FMA)
fmu_twp <- read.csv(file ='../data/FMU_TWP.csv')
species_prop <- read.csv(file = '../data/species_proportions_full.csv') %>%
  select(TRM,max_species)

@@

util_piece <-full_join(util_std,piece_size,by=c("FMU","CD"))
util_piece_fmu_twp <- full_join(util_piece,fmu_twp,by=c("FMU","CD"))
util_piece_fmu_twp$piece_size <- signif(1/util_piece_fmu_twp$logspm3,3)
util_piece_fmu_twp_species <- full_join(util_piece_fmu_twp,species_prop,by="TRM")
util_piece_fmu_twp_species <- subset(util_piece_fmu_twp_species, (FMU != "A14") &(FMU != "A15") &(FMU != "W11")& (FMU != "W13"))

subs <- subset(util_piece_fmu_twp, (!is.na(piece_size)) & (!is.na(areaha)) & (CD == "Decid"))
avepieceD <- signif(weighted.mean(subs$piece_size,subs$areaha,na.rm = TRUE),3)

subs <- subset(util_piece_fmu_twp, (!is.na(piece_size)) & (!is.na(areaha)) & (CD == "Conif"))
avepieceC <- signif(weighted.mean(subs$piece_size,subs$areaha,na.rm = TRUE),3)
